Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2015-07-08 paper/letter.tex
update

TOL1214-277 Blue Compact Dwarf Galaxy

Star forming galaxy, no old stars.

>>>>

TOL1214-277 was first observed by ... it is a compact 
dwarf galaxy and does not have old stars.

The Ly$\alpha$ emission line was first observed in the TOL1214-277 
galaxy by \citep{Thuan97}. It has two main important features which 
make this a very uncommun LAE. First it shown a symmetric profile 
which is , Second the Ly$\alpha$ line is not shifted with respect to 
the H$\beta$ line.  Blue compact Dwarf Galaxy
